% ============================ Listing definitions =============================
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{ip}{
    numberstyle=\tiny\color{codegray},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2,
    frame=single,
    numbers=none,
}
\lstset{style=ip}
% ==============================================================================

\begin{filecontents*}{sc-mdp.txt}
action(left) :- in_s_1.    action(right) :- not in_s_1.
\end{filecontents*}

\begin{filecontents*}{sc-pomdp.txt}
0.041::action(left) ; 0.959::action(right) :- left_wall_present, \+ right_wall_present.
0.581::action(left) ; 0.419::action(right) :- \+ left_wall_present, \+ right_wall_present.
\end{filecontents*}

\begin{filecontents*}{dc-asp.txt}
action(turn_right) :- a_5, a_8.
action(forward) :- a_2.
action(toggle) :- a_3.
% Definitions of each invented predicate a_i:
a_2 :- top_right_corner_wall.
a_3 :- one_step_ahead_closed_door.
a_5 :- not curr_location_open_door,
        not one_step_ahead_closed_door.
a_8 :- two_step_ahead_unseen.
\end{filecontents*}


\begin{filecontents*}{dct-asp.txt}
action(turn_right) :- a_5, a_8.
action(forward) :- not a_1, a_2.
action(toggle) :- a_3.
action(toggle) :- a_1, not a_3, a_12.
\end{filecontents*}

\begin{filecontents*}{dcot-asp.txt}
action(turn_right) :- a_5, a_8, a_11.
action(forward) :- a_2.
action(toggle) :- a_3.
action(toggle) :- not a_2, not a_3, not a_11.
\end{filecontents*}
